Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-10-25 Ch1_movement_rates/Ch1_Figures.Rmd
Figure 2 shows distribution of movement rates for the "population" and the social groups.

```{r}
# Visualize distribution and data points
#vlines <- summary(indiv_moverate$movrate)[c(1,3,6)]
cols.fig2 <- c("#23262f","#717492","#b3a82a","#c94f21","#980012","#0d907a","#b9bec3")

indiv_moverate %>%
  ggplot(., aes(x = movrate, y = 0.002, color = fam_g)) +
  geom_point(size = 3, alpha = 0.8) +
  # geom_point(data = fam_moverate, aes(x = movrate, y = 0.004),size = 3, alpha = 0.8, color = my.cols1[4]) +
  stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),
                color = "black", alpha = 0.8, size = 1) +
  scale_color_manual(values = cols.fig2) +
  labs(x = "Movement Rate (meters/minute)", y = "Density",
       title = "Lognormal fit to individual movement rates") +
  #geom_vline(xintercept = vlines, color = my.cols1[4], size = 1, lty = 2) +
  scale_x_continuous(limits = c(0, 70)) +
  #scale_x_discrete(labels = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60)) +
  guides(color = guide_legend(title = "Social Group",
                              ncol = 2)) +
  theme_bw() +
  theme(legend.position = c(0.8, 0.6))

# ggsave2(filename = "Ch1_movement_rates/Figures/logfit_cp.png")
```

>>>>

```{r fig.height=12}
# Visualize distribution and data points

load("Ch1_movement_rates/sims_backup/movrates.RData")

cols.fig2 <- c("#23262f","#717492","#b3a82a","#c94f21","#980012","#0d907a","#b9bec3")

indiv_moverate %>%
  ggplot(., aes(x = movrate, y = 0.002, color = fam_g)) +
  geom_point(size = 3, alpha = 0.8) +
  # geom_point(data = fam_moverate, aes(x = movrate, y = 0.004),size = 3, alpha = 0.8, color = my.cols1[4]) +
  stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),
                color = "black", alpha = 0.8, size = 1) +
  scale_color_manual(values = cols.fig2) +
  labs(x = "Movement Rate (meters/minute)", y = "Density",
       title = "Lognormal fit to individual movement rates") +
  #geom_vline(xintercept = vlines, color = my.cols1[4], size = 1, lty = 2) +
  scale_x_continuous(limits = c(0, 70)) +
  #scale_x_discrete(labels = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60)) +
  guides(color = guide_legend(title = "Social Group",
                              ncol = 2)) +
  theme_bw() +
  theme(legend.position = c(0.8, 0.6)) -> logfit_plot

# Estimate the mu's for each family group based on their movement rate.
logfit.sigma <- logfit$estimate[2]
get_mu <- function(movrate, sigma = logfit.sigma){
  mu <- log(movrate)-((sigma^2)/2)
  return(mu)
}

fam_mus <- get_mu(fam_moverate$movrate)

glines <- purrr::map(1:7, function(y)
    stat_function(fun = dlnorm, args = list(meanlog = fam_mus[y], sdlog = logfit.sigma), color = cols.fig2[y]))

fam_moverate %>%
  ggplot(., aes(x = movrate, y = -0.002, color = fam_g)) +
  geom_point(size = 3, alpha = 0.8) +
  glines +
  scale_color_manual(values = cols.fig2) +
  labs(x = "Movement Rate (meters/minute)", y = "Density",
       title = "Distribution for social group movement rates") +
  #geom_vline(xintercept = vlines, color = my.cols1[4], size = 1, lty = 2) +
  scale_x_continuous(limits = c(0, 70)) +
  #scale_x_discrete(labels = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60)) +
  guides(color = guide_legend(title = "Social Group",
                              ncol = 2)) +
  theme_bw() +
  theme(legend.position = c(0.8, 0.6)) -> social_group_curves

plot_grid(logfit_plot, social_group_curves, nrow = 2)

# ggsave2(filename = "Ch1_movement_rates/Figures/Figure2.png")
